{Slate is a bla bla.}



\section{Description of the Problem}

\begin{itemize}
	\item \hl{Give an overview of the problem area and your specific problem that you aim to solve.}
	\item \hl{If necessary, provide a literature survey, that is who has done what in this specific problem area, with references to bibliographic resources.}
	\item \hl{If there already exists a number of solutions/products related to your specific problem, present a comparative evaluation of these solutions/products.}
	\item \hl{State that a detailed description of the problem is provided in Appendix A: Requirement Specifications Document.}
\end{itemize}


\section{Project Goal(s)}

\begin{itemize}
	\item \hl{Goal(s) of your project}
	\item \hl{Basically extracted from Section 1.1 of this report.}
	\item \hl{For example: ``To develop a prototype, a model, a software product, a hardware product, a hardware/software product, a process, etc. in \ldots''}
\end{itemize}

\section{Project Output(s)}

\begin{itemize}
	\item \hl{Give a list of all project outputs for COMP 4910.}
	\item \hl{Also, provide a list of predicted additional outputs for COMP 4920.}
	\item \hl{When completed, your project outputs are a software product or a hardware product or a hardware/software product, with all the associated documents such as RSD's, DSD's and PM.}
\end{itemize}


\section{Project Activities and Schedule}


\begin{itemize}
	\item \hl{Your activities and schedule for COMP 4910 activities}
	\item \hl{Also, your planned activities and schedule for COMP 4920 activities}
	\item \hl{For example: Produce first version of problem definition, our 4910 project assignment form, then produce RSD v1.0, then DSD v1.0 as high level design, then DSD v2.0 as detailed design, then implementation and testing activities, then PM, etc}
\end{itemize}

