\hl{A concþusion text for your project goes here.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}

\begin{itemize}
	\item \hl{Summary of your project}
	\item \hl{Discuss what you have done so far.}
\end{itemize}

\ac{ECC} is an acronym.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cost Analysis}

\begin{itemize}
	\item \hl{Manpower spent in your project: In man-days, for each team member, per month and total. Assume one man-day means ``actually working" for 8 hours, excluding any breaks. Provide a detailed table showing manpower for each month and for each team member and also totals for each month, each team member and overall manpower effort.}
	\item \hl{Any hardware and/or software you bought or consider to buy for your project. Provide a detailed table including item, brand name, model, properties and cost.}
	\item \hl{Perform a simple cost analysis based on information you provide.}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Benefits of the Project}

\begin{itemize}
	\item \hl{Benefits of your product to its users, to human kind, to animals, to plants, to nature, etc.}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}

\begin{itemize}
	\item \hl{What can be added to your project in future, in terms of additional functionality, more performance, larger or different data, etc.}
	\item \hl{You should certainly explain what is to be completed in COMP 4920.}
	\item \hl{You are also advised to consider other possible additions to your project which can be done after COMP 4920.}
\end{itemize}

